Paper_analyses

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

?car::scatter3d
View(clustering_agg)
clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))
car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          # point = FALSE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )

>>>>

?car::scatter3d
View(clustering_agg)
clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))

clustering_agg2$y_kmeans<- as.factor(as.character(clustering_agg2$y_kmeans))

car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          # point = FALSE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )

clustering_agg2$AlexGroup<-as.factor(clustering_agg2$AlexGroup)
clustering_agg2<- subset(clustering_agg2, !is.na(stimDescription))
car::scatter3d(clustering_agg2$log_Bio_CDA.PhasicMax_z, 
          clustering_agg2$Bio_Mean_HR_dif_z, 
          clustering_agg2$pup_basCor_z,
          fit = "smooth",
          # point = FALSE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg2$AlexGroup
          # point.col = clustering_agg2$y_kmeans
          )
